NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-18 intro.tex
update setup

The precise understanding of the electroweak symmetry breaking mechanism is an important cornerstone in verifying the
Standard Model. Different realizations of the electroweak sector or new physics coupling to electroweak gauge bosons will
yield to deviations compared to the Standard Model prediction. New physics effects can conveniently be described in terms
of an effective theory where new heavy degrees of freedom are integrated out and deviations from the Standard Model are 
parametrised by higher dimensional operators \cite{Weinberg:1978kz,Weinberg:1979pi}. Higher dimensional operators can lead
 to deviations in triple and quartic gauge couplings. Moreover, new vertices (e.g. $Z\gamma\gamma$) that do not exist in the 
Standard Model can appear. The class of processes that involve a pair of photons in association with another vector boson
allows to measure deviations in triple and quartic gauge couplings and is therefore a particularly interesting class of processes.
 Consequently both ATLAS and CMS have measured these type of processes und derived constraints on anomalous gauge
 couplings \cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}.\\
 In this paper we calculate the next-to-leading order QCD and electroweak corrections to the processes 
 $\gamma\gamma\gamma$, $\gamma\gamma e^{+} e^{-}$ and $\gamma\gamma e^{-} \bar{\nu_e}$. For the latter two, all
 possible off-shell contributions are taken into account. The QCD corrections to these processes are already known 
 \cite{Bozzi:2011en,Campbell:2012ft,Bozzi:2011wwa}. For a more complete picture of the higher order effects we also
% recalculate the QCD corrections for a center of mass energy of $13$ TeV, and supplement them with the 
% next-to-leading order electroweak corrections.

>>>>

The precise understanding of the electroweak symmetry breaking mechanism is an important cornerstone in verifying the
Standard Model. Different realizations of the electroweak sector or new physics coupling to electroweak gauge bosons will
yield to deviations compared to the Standard Model prediction. New physics effects can conveniently be described in terms
of an effective theory where new heavy degrees of freedom are integrated out and deviations from the Standard Model are 
parametrised by higher dimensional operators \cite{Weinberg:1978kz,Weinberg:1979pi}. Higher dimensional operators can lead
 to deviations in triple and quartic gauge couplings. Moreover, new vertices (e.g. $Z\gamma\gamma$) that do not exist in the 
Standard Model can appear. The class of processes that involve a pair of photons in association with another vector boson
allows to measure deviations in triple and quartic gauge couplings and is therefore a particularly interesting class of processes.
 Consequently both ATLAS and CMS have measured these type of processes und derived constraints on anomalous gauge
 couplings \cite{Aad:2016sau,Sirunyan:2017lvq,Aad:2015uqa,Aad:2015bua}.\\
 In this paper we calculate the next-to-leading order QCD and electroweak corrections to the processes 
 $\gamma\gamma\gamma$, $\gamma\gamma e^{+} e^{-}$ and $\gamma\gamma e^{-} \bar{\nu_e}$. For the latter two, all
 possible off-shell contributions are taken into account. The QCD corrections to these processes are already known 
 \cite{Bozzi:2011en,Campbell:2012ft,Bozzi:2011wwa}. For a more complete picture of the higher order effects we also
recalculate the QCD corrections for a center of mass energy of $13$ TeV, and supplement them with the 
 next-to-leading order electroweak corrections. Although the electroweak corrections are much smaller at the level
 of the total cross section compared to the NLO QCD corrections they are particularly important when deriving limits on 
 anomalous couplings. The effects of higher dimensional operators increase in the high energy tails of differential distributions
 and lead to a change of the shapes. And it is in the same region where the Sudakov logarithms from the electroweak
 corrections will play an essential role as well.\\
 The paper is organized as follows. In section \ref{sec:setup} we describe the calculational setup that has been used to obtain our
 numerical result which we are going to discuss in section \ref{sec:results} before we conclude in section \ref{sec:conclusions}.

### 2017-10-18 setup.tex
aaa plots in draft, need refinement
update setup

\section{Calculational setup}
\label{sec:setup}

We do it in a way that works.

>>>>

\section{Calculational setup}
\label{sec:setup}
The results presented in this paper have been obtained by combining the two tools
\GoSam~\cite{Cullen:2011ac,Cullen:2014yla} and \Sherpa~\cite{Gleisberg:2008ta}
which allows for a fully automated calculation of cross section and observables and next-to-leading order in QCD as well
as in the electroweak coupling.
\GoSam is a package which generates the code for the numerical evaluation of
the one loop scattering amplitudes starting from the Feynman diagrams,
generated with \QGraf~\cite{Nogueira:1991ex} and further processed with
\FORM~\cite{Vermaseren:2000nd,Kuipers:2012rf} and
\Spinney~\cite{Cullen:2010jv} to perform necessary algebraic
manipulations to obtain an optimized expression for the matrix elements.
For the integrand reduction of the diagrams we use the \Ninja
library~\cite{Peraro:2014cba}, an implementation of the technique of integrand
reduction via Laurent expansion~\cite{Mastrolia:2012bu,vanDeurzen:2013saa}.
Alternatively one can choose other reduction strategies such as OPP reduction
method~\cite{Ossola:2006us,Mastrolia:2008jb,Ossola:2008xq} which is
implemented in $d$ dimensions in \Samurai~\cite{Mastrolia:2010nb}, or methods based on
tensor integral reduction as implemented in
\GolemNF~\cite{Heinrich:2010ax,Binoth:2008uq,Cullen:2011kv,Guillet:2013msa}.
We have used \OneLoop~\cite{vanHameren:2010cp} to evaluate the scalar integrals.

We define our central scales through
\begin{equation}
  \label{eq:murfdef}
  \begin{split}
    \muR^0 = \muF^0 = \ldots
  \end{split}
\end{equation}
and subsequently vary them by the conventional factor 
of two to estimate higher order contributions.
